--- 
title: "Natural Language Processing"
author: "Shivam Upadhyay"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
description: |
  This is a minimal example.
link-citations: yes
url: 'https\://bookdown.org/shivam7898/NLP'
github-repo: "shivam7898/NLP"
subtitle: "R and Python"
---

# About {#FIRST .unnumbered} 
[Goto LAST](#LAST "End of the Document")

\textcolor{pink}{Caution:}  
The HTML File access MathJax via internet to render LaTeX Equations. Thus, equations will NOT be rendered properly if the file is viewed offline. Otherwise, the file is a standalone document containing all the relevant images, tables and codes to generate them.

## Preface {.unnumbered}

This repository contains notes, codes, models, and output for Natural Language Processing (NLP) using R and Python.

Proper reference to the original source may sometimes be lacking. This is regrettable and these references will be included in later versions.

The current status of the document is 'work-in-progress' as it is incomplete and it may contain inconsistencies and errors. 

Shivam Upadhyay

****


## Environment {.unnumbered .tabset .tabset-fade}

\textcolor{pink}{Assumption: Working directory has sub-folders named "data", "images", "code", "docs".}

<!-- This is a comment. -->

```{r '000A', include=FALSE, cache=FALSE}
# #Knitr Setup, Packages, Functions. Each checks the environment and runs only once.
sys.source(here::here("code", "A00Knitr.R"), envir = knitr::knit_global())
sys.source(here::here("code", "A01Packages.R"), envir = knitr::knit_global())
sys.source(here::here("code", "A02AllUDF.R"), envir = knitr::knit_global())
```

### R Version {.unlisted .unnumbered}

```{r '000B-RVersion'}
# #R Version
R.version.string
```  

### Working Directory {.unlisted .unnumbered}

```{r '000C-Directory'}
# #Working Directory
getwd()
```

### Session Info {.unlisted .unnumbered}

```{r '000D-Session'}
# #Version information about R, the OS and attached or loaded packages
sessionInfo()
``` 
 
### Pandoc {.unlisted .unnumbered}

```{r '000E-Pandoc'}
# #Pandoc Version being used by RStudio
rmarkdown::pandoc_version()
```  

```{r '000F-Bib', include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


## Validation {.unlisted .unnumbered .tabset .tabset-fade}

```{r '000X-Cleanup', include=FALSE, cache=FALSE}
if(TRUE) f_rmExist(aa, bb, ii, jj, kk, ll)
```

```{r '000Z-Validation', include=TRUE, cache=FALSE}
# #SUMMARISED Packages and Objects (BOOK CHECK)
f_()
#
difftime(Sys.time(), q_start)
```


****
